BOLD Parameter Estimation Using Particle Filters

### 2010-07-05 doc/thesis/results.tex
work on particle filter.
almost done with methods
some changes to methods
some mild additions to methods and results

\chapter{Results}
\section{Single Time-Series Simulation}

@@

>>>>

\chapter{Results}
\section{Single-Voxel Simulation}
The results

\section{Single-Voxel Analysis}
This section discusses the results when the particle filter was
applied on a single voxel. The parameters are the same as
those used later for entire image analysis; however, the results
are more in-depth.

The run-time for a single voxel depends on the several factors. First, the
overall length of the signal being analyzed. For 1000 measurements it takes
about 10 to 15 minutes. On the other hand, in real circumstances the
length is only around 150 measurements. The number of  integration
can certainly make a large difference, however dropping below 1000 (.001 seconds)
is definitely not recommended.

For a period I considered 1000 to be a
fine number; however when generating simulated data I found that every once
in a while 1000 was not enough. This is problematic in the actual particle
filter since, given the large number of simultaneous integrations taking 
place, its likely that a few particles will fail and be weighted at 0 because
of this problem. Additionally, because the typical case where a failure would
occur is at fast moving times/parameters the particles all tend to fail together.
The result is particle deprivation - no particles with non-zero weights remain.
The other possible outcome is that low time constant particles get pruned resulting
in excessively smoothed estimates for the time series'. Its possible that a
kind of stop-gap measure could be put into place; wherein particles that are
about to be set to NaN are integrated again with finer grained steps. However
many times the non-real results don't occur until several time steps after the 
numbers get strange. So for instance, the timestep was too long, allowing 
$f$ to go negative, resulting in extremely large values of $q$. There are many
different ways where this sort of event can occur, and unfortunately sometimes
there is no way to get back to before the state starting going out of control.

Another crucial factor to run time is how long before the first re-sampling 
occurs. Because the prior is represented initially with significantly more
particles, if the model fits very well, or for some reason the effective
number of particles stays high, resampling could take a long time to occur.
When this happens the particles filter can take a factor of 10 longer to run.
However, if the particle count isn't initially set high, there is a much larger
chance of particle deprivation occurring. Since there is no real way to know
how long it will take to resmaple the first time, there is little the 
algorithm can do to fix this. On the other end of the specture, if the time
series don't match the model at all, particle deprivation will occur extremely
quickly, and even the recovery technique discussed in \autoref{sec:Resampling}
won't help. The upshot of this is that the particle filter is able to 
identify these sections very quickly, and thus not waste much time there.
Of course, if a fat-tailed distribution is used for the weighting function,
or the standard deviation of a Gaussian weighting function is very large,
the particle filter will simply converge to meaningless values.

\begin{figure}
\caption{Particle Filter converging to values that make little sense,
because the voxel did not correlate with the input in any known way}
\end{figure}

\section{Weighting Function Comparison}
\label{sec:Results Weights}

\section{Single Time-Series Simulation}

@@

Final parameter distribution among active regions.
Q-Q plots?
